Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

This motivates the following interlacing connection structure between
levels. For each level in the info-graph, there are $\NG^2$ groups for
some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,\ldots,L\}$
and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
visualization of simple case with $\NG = 2$). Two observations are
in order:
% \OMIT{(i) The number of groups does not grow with $L$ and stays as
%   $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
%   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
\begin{itemize}
\item[(i)] Consider level $(l - 1)$ and fix the last group index to be
  $v$, and consider the set of groups
  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
  and $G_{l-1,2,1}$ circled in the Figure
  \ref{fig:llevel-connecting}). The agents in any group of
  $\cG_{l-1, v}$ observe the same sub-history. If the empirical mean
  of arm $a$ is sufficiently high in their shared sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky'' groups for $a$.

>>>>

This motivates the following interlacing connection structure between
levels. For each level in the info-graph, there are $\NG^2$ groups for
some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,\ldots,L\}$
and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
visualization of simple case with $\NG = 2$). Two observations are
in order:
% \OMIT{(i) The number of groups does not grow with $L$ and stays as
%   $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
%   incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
\begin{itemize}
\item[(i)] Consider level $(l - 1)$ and fix the last group index to be
  $v$, and consider the set of groups
  $\cG_{l-1, v}=\{G_{l-1,i,v}\mid i \in [\NG]\}$ (e.g. $G_{l-1,1,1}$
  and $G_{l-1,2,1}$ circled in red in the Figure
  \ref{fig:llevel-connecting}). The agents in any group of
  $\cG_{l-1, v}$ observe the same sub-history. As a result, if the
  empirical mean of arm $a$ is sufficiently high in their shared
  sub-history, then all groups in $\cG_{l-1, v}$ will become ``lucky''
  for $a$.
